formula1

### 2020-05-18 inst/formula1.Rmd
load vars here

```{r,polepositionlikelihood,cache=TRUE}
HP <- hyper2(pnames=c(rownames(f2017),"pole"))
noscore <- c("Ret", "WD", "DNS", "DSQ", "DNP", "NC")

for(i in seq_len(ncol(f2017))){
	y <- f2017[,i]
	if(any(y %in% noscore)){y[y%in%noscore] <- 0}
	y <- as.numeric(levels(y)[y])
	names(y) <- rownames(f2017)
	HP <- HP + pwa(ordervec2supp(y),details$pole[i],"pole")
} # i loop closes
head(HP)
(mHP <- maxp(HP))
pie(mHP)
```

>>>>

```{r,polepositionlikelihood,cache=TRUE}
f2017 <- read.table("formula1_2017.txt",header=TRUE)
details <- read.table("formula1_conditions.txt",header=TRUE)
HP <- hyper2(pnames=c(rownames(f2017),"pole"))
noscore <- c("Ret", "WD", "DNS", "DSQ", "DNP", "NC")

for(i in seq_len(ncol(f2017)-1)){
	y <- f2017[,i]
	if(any(y %in% noscore)){y[y%in%noscore] <- 0}
	y <- as.numeric(levels(y)[y])
	names(y) <- rownames(f2017)
	HP <- HP + pwa(ordervec2supp(y),details$pole[i],"pole")
} # i loop closes
head(HP)
(mHP <- maxp(HP))
pie(mHP)
```
